Rbans-output

### 2020-11-06 reports/interactive-rbans.Rmd
Adds updated report with standardized scores

df_rbans_long <- df_rbans_long %>%
  arrange(rbansid, session)
```

@@

Row {data-height=400}
---------------------------
### Visualisation of RBANS in different sessions
```{r}
selection_widget <- bscols(
  widths = 6,
  filter_select("subtest", "Subtest", shared_rbans, ~subtest, multiple = FALSE),
  filter_select("first_training", "Group", shared_rbans, ~first_training, multiple = FALSE)
)
selection_widget
```

@@

```{r}
plot_ly(shared_rbans, x = ~session, y = ~score) %>%
  add_trace(type = "box",  color = ~as.factor(session),
            hoverinfo = "y", showlegend = TRUE, boxmean = TRUE) %>%
  layout(showlegend = FALSE, autosize = TRUE, height = 500)
```

@@

```{r}
plot_ly(shared_rbans, x = ~session, y = ~score) %>%
  add_trace(type = "scatter", x=~session, y = ~score,
            mode = "lines+markers", split = ~rbansid) %>%
  layout(showlegend = FALSE, autosize = TRUE, height = 500)
```

```{r eval = FALSE}
df_rbans_long %>%
  filter(subtest == "iq_celek") %>%
  filter(first_training == "TP") %>%
  plot_ly(x= ~session, y = ~score) %>%
   add_trace(type = "box",  color = ~as.factor(session),
            hoverinfo = "y", showlegend = TRUE, boxmean = TRUE) %>%
  add_trace(type = "scatter", y = ~score,
            mode = "lines+markers", split = ~rbansid) %>%
  layout(showlegend=FALSE)
````

>>>>

df_rbans_long <- df_rbans_long %>%
  arrange(rbansid, session)

df_rbans_long <- df_rbans_long %>%
  group_by(session, subtest) %>%
  mutate(scaled_score = (score-mean(score, na.rm = TRUE))/sd(score, na.rm = TRUE)) %>%
  ungroup()
```

@@

Row {data-height=300}
---------------------------
### Visualisation of RBANS in different sessions
```{r}
selection_widget <- bscols(
  widths = 6,
  filter_select("subtest", "Subtest", shared_rbans, ~subtest, multiple = FALSE),
  filter_select("first_training", "Group", shared_rbans, ~first_training, multiple = FALSE)
)
selection_widget
```

@@

```{r}
plot_ly(shared_rbans, x = ~session, y = ~scaled_score) %>%
  add_trace(type = "box",  color = ~as.factor(session),
            hoverinfo = "y", showlegend = TRUE, boxmean = TRUE) %>%
  layout(showlegend = FALSE, autosize = TRUE, height = 500)
```

@@

```{r}
plot_ly(shared_rbans, x = ~session, y = ~scaled_score) %>%
  add_trace(type = "scatter", x=~session, y = ~scaled_score,
            mode = "lines+markers", split = ~rbansid) %>%
  layout(showlegend = FALSE, autosize = TRUE, height = 500)
```

```{r eval = FALSE}
df_rbans_long %>%
  filter(subtest == "iq_celek") %>%
  filter(first_training == "TP") %>%
  plot_ly(x= ~session, y = ~scaled_score) %>%
   add_trace(type = "box",  color = ~as.factor(session),
            hoverinfo = "y", showlegend = TRUE, boxmean = TRUE) %>%
  add_trace(type = "scatter", y = ~scaled_score,
            mode = "lines+markers", split = ~rbansid) %>%
  layout(showlegend=FALSE)
````

### 2020-11-06 reports/rbans-output.Rmd
Adds updated report with standardized scores

df_rbans %>%
  filter(diagnosis == "schizophrenia") %>%
  ggplot(aes(session, iq_rec)) +
    geom_line(aes(color=rbansid)) +geom_point() +
    facet_wrap(~first_training)

>>>>

df_rbans %>%
  filter(!is.na(first_training)) %>%
  ggplot(aes(session, iq_rec)) +
    geom_line(aes(color=rbansid)) + geom_point() +
    facet_wrap(~c(first_training, diagnosis))
